\documentclass[11pt]{article}

\usepackage{changepage}
\usepackage{amsmath}
\usepackage[a4paper, total={7.25in, 10in}]{geometry}
\usepackage{url}
\usepackage{indentfirst}
\usepackage{hanging}
\usepackage[document]{ragged2e}
\usepackage[notes, short, backend=biber]{biblatex-chicago}
\usepackage{cmsendnotes}
\usepackage{hyperref}

\setlength{\parindent}{0pt}
\setlength{\RaggedRightParindent}{0pt}
\setlength{\parskip}{1em}

\newcommand{\BExcerpt}{}
\newcommand{\EExcerpt}{}

\title{Wolftree}
\date{7 November 2024}

\begin{document}
    \maketitle
    \BExcerpt
    It's colder here like you wanted (but still, not by much). The thrift store in the visitor's center has been closed since five. A plastic flamingo (\$19.50 from Walmart, incl. tax, for a two-pack) (I wore one on my head for Halloween this year) stands on the ice machine. Somebody sits between us with the hair of an old friend -- they catch me looking but really I'm just searching for the sibling. My drink is the Bittersweet Symphony, named for a song that's followed us (more me than you) since I was seventeen. It was dark when I arrived and is darker when I leave. I stand at the curb and motion the old man to drive on ahead -- he parodies the gesture but you know I don't trust like that. Seven miles up, a bar with twenty-four open seats. Stock photos of cocktails (three per) splashing in their glasses against a black void. Inexplicably, The Beatles too. The bartender says sorry like you imagine a Canadian might. A man tells me he's writing a novel about his cats and it's making him so happy. You ask me what it's like to not be such a hometown guy, and we laugh but you were always crueler than you let on.
    \EExcerpt
\end{document}
